Seminar paper on Probabilistic Near-Duplicate Detection Using Simhash

### 2019-07-09 ii/paper/paper.tex
Done

\subsection{Online Mode}

>>>>

\subsection{Probabilistic Simhash Matching}

The VOSH algorithm is implemented in a framework called Probabilistic Simhash Matching (PSM).
PSM features an online mode, in which all existing Fingerprints are stored in a collection $H$.
$H$ is sorted before the algorithm start, therefore the cost for sorting the set are not considered here.

Since using VOSH on all bites and the whole dataset $H$ is highly inefficient only a small range of bits.
The search is then performed on a small range of uppermost bits, which are called headers.
For the purpose of performant header lookups a hash table of size $t$ is used as can be seen in Figure~\ref{fig:vosh-lookup}.

\begin{figure}[h]
    \includegraphics[scale=0.33]{./gfx/vosh-online.png}
    \centering
    \caption{The lookup using PSM is not performed on the whole dataset $H$, but rather on a small subset of bits defined by the header in the hash table.}\label{fig:vosh-lookup}
\end{figure}

The algorithm also features a batch query mode, which accumulates new fingerprints in a set $Q$, until it reaches size $m$.
Once the threshold is reached, PSM splits the existing collection in chunks of $m$ fingerprints and matches each $x \in Q$ against the loaded chunk.
Afterwards all $x \in Q$ are sorted and appended to the existing collection.

\section{Conclusion}
The authors of~\cite{inproc:main} compare their proposed methodology to the, at their time, most performant implementation, namely Block-Permuted Hamming Search (BPHS), for finding similar \emph{simhashes} in a document collection~\cite{Manku:2007:DNW:1242572.1242592}.

\begin{figure}[H]
    \includegraphics[scale=0.4]{./gfx/performance_comparison.png}
    \centering
    \caption{Performance comparison between PSM and BPHS in batch mode.}\label{fig:performance-comparison}
\end{figure}

PSM outperforms BPHS in pretty much every scenario, by sacrificing a very small amount of recall.
This new approach can be seen as a viable addition for \emph{simhashing} algorithms.
